%====================
% Current Role, CADCAM Software
%====================
\subsection{{Software Engineer Senior \hfill May 2022 - Present}}
\subtext{Lockheed Martin \hfill Fort Worth, TX}
\begin{zitemize}
\item Implement automated pipelines for Catia V5 and 3DX (V6) customizations using GitLab Pipelines used across the CAD/CAM organization.
\item Design and implement continuous integration/continuous development  processes for CAD/CAM applications to air-gaped networks and unclassified networks.\\
\item Standardize packages and deployments to company network and closed areas.
\item Develop and support applications that configure Catia 3DX and V5 environments with proprietary software and settings.
\item Architect Catia V5 and 3DX environments with proprietary software, 3rd party applications, and cooperate settings, giving Lockheed designers an edge on the competition. 
\item Manage coding standards and approve code reviews for development of 3dx and V5 custom applications\\
\end{zitemize}

%====================
% ML/AI training at Lockheed
%====================
\subsection{{Machine Learning/AI at Lockheed Study Group \hfill April 2023-May 2023}}
\subtext{Lockheed Martin \hfill Fort Worth, TX}
\begin{zitemize}
\item Attended classes led by Lockheed Martin professionals teaching the fundamentals of Data Science using the company's preferred tool sets.
\item Collaborated with colleagues inside Lockheed Martin to solve sample problems in Data Science.
\end{zitemize}

%====================
% CDN Roll
%====================
\subsection{{Software Engineer \hfill July 2018 - May 2022}}
\subtext{Lockheed Martin \hfill Fort Worth, TX}
\begin{zitemize}
\item Maintained an application for releasing design engineer's drawings and 3-D models. Leveraged an Oracle database for storing the CAD Data, meta-data parts and positions on different airplanes, and release state of drawings.
\item Developed features for designers to create retro-fit 3-D models to mimic elements of a previously designed mod-kit drawings and modify spacial query functions to consider the instructions when querying 3-D space.
\item Supported the effort to migrate programs from outdated Catia V4 systems into our Catia V5 system for drawing release and 3-D design. Specifically, support processes that make this an easy transition for legacy programs.
\end{zitemize}

%====================
% Internship
%====================
\subsection{{Software Engineer Intern \hfill May 2017 - Aug 2017}}
\subtext{Inmar \hfill Fort Worth, TX}
\begin{zitemize}
\item Translated complex Microsoft SQL logic in stored procedures to SQL Server Integration Service (SSIS) packages for daily loads from a real-time database (Informix) to a long term Data Warehouse (Microsoft SQL).
\item Wrote SQL Server Reporting Services (SSRS) dashboards to report on long term error trends in the daily loads to enable development teams to anticipate potential problems.
\end{zitemize}

